### 2024-06-15 conteudo/tool/architecture.tex
Add some work, 15/06

There is a example of each file in the Appendix

@@

@@

>>>>

@@

The Setup step is a procedure executed by the user once per codebase. The Setup step receives the input codebase and the minimum
similarity metric value to a pair of functions to be considered a duplication, then it executes the Function Parser and the Code 
Duplication Finder, to generate the temporary codebase and the Code Duplication Database, which will be later used by the Query
Responder step. The value of the minimum similarity metric is to reduce the Code Duplication Database, which optimize the
memory usage and the computational cost of the Query Responder step. For example, if this parameter does not exist and we work in 
a codebase of $10000$ functions and supposing each relative path plus the function name have $50$ charactes, the Code Duplication 
Database will be a file of size approximately $5000^2 \times 50 ~= 5$ Gigabytes, as it is not expected to a real large codebase 
to the majority of pairs of functions be a duplication of each other, this number can be reduced dramastically.

@@

The Query Responder step is the component that the user executes multiples times to consult information about code duplication in
a codebase that was previously preprocessed by the Setup step. The Query Responder step consumes the temporary codebase and the 
Code Duplication Database created by the Setup step. This component implements all the tool's functionalities exposed 
for the user, which are described in the \ref{subsec:func}.
